### 2024-07-19 basic-statistics.qmd
20240719 - summary of statistical decision trees

An example statistical decision tree is depicted in @fig-statisticalDecisionTree.

@@

@@

>>>>

A statistical decision tree is a flowchart or decision tree that depicts which statistical test to use given the purpose of analysis, the type of data, etc.
An example statistical decision tree is depicted in @fig-statisticalDecisionTree.

@@

This statistical decision tree can be generally summarized such that associations are examined with the correlation/regression family, and differences are examined with the *t*-test/ANOVA family, as depicted in @fig-statisticalDecisionTreeSummary.

::: {#fig-statisticalDecisionTreeSummary}
![](images/statisticalDecisionTreeSummary.png)

Summary of A Statistical Decision Tree For Choosing an Appropriate Statistical Procedure.
:::

@@

Both associations and differences can be examined with the regression family, which greatly simplifies our summary of the statistical decision tree, as depicted in @fig-statisticalDecisionTreeSummaryRegression.

::: {#fig-statisticalDecisionTreeSummaryRegression}
![](images/statisticalDecisionTreeSummaryRegression.png)

Summary of A Statistical Decision Tree For Choosing an Appropriate Statistical Procedure.
:::

Thus, in most cases, the regression framework can be used to examine most questions regarding associations between variables or differences between groups.
